manuscript_figures

### 2024-06-06 scripts/manuscript_figures.Rmd
updated stats for correlation analysis and made plot

# Load libraries 
```{r}
library(plyr)
library(dplyr)
library(tigris)
library(car)
library(MuMIn)
library(lmerTest)
library(tidyverse)
library(lme4)
library(broom.mixed)
library(ggmap)
library(lubridate)
library(ggplot2)
library(PerformanceAnalytics)
library(reshape2)
library(viridis)
library(GGally)
library(corrplot)
library(patchwork)
library(broom)
library(ggspatial)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggspatial)

@@

# Figure 5: Multiple regression (correlation analysis) between fish biomass (g/m2), kelp biomass (g/m2), kelp cover, rugosity, temperature in ggplot 
# combine all dataframes
```{r}
# left join can only combine two at a time
# combing kelp cover and fish biomass
master.dat1 <- left_join(kelp.filt, fish.filt)

@@

ggsave(filename = "output/figures/figure_5.png", device = "png", width = 10, height = 10)
```

>>>>

# Load libraries 
```{r}
library(plyr)
library(dplyr)
library(tigris)
library(htmlwidgets)
library(car)
library(MuMIn)
library(lmerTest)
library(tidyverse)
library(lme4)
library(broom.mixed)
library(ggmap)
library(lubridate)
library(cowplot)
library(ggplot2)
library(PerformanceAnalytics)
library(reshape2)
library(viridis)
library(GGally)
library(corrplot)
library(patchwork)
library(broom)
library(ggspatial)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggspatial)

@@

# Figure 5: Correlation analysis between fish biomass (g/m2), kelp biomass (g/m2), kelp cover, rugosity, temperature in ggplot 
# combine all dataframes
```{r}
# left join can only combine two at a time
# combing kelp cover and fish biomass
master.dat1 <- left_join(kelp.filt, fish.filt)

@@

ggsave(filename = "output/figures/correlation_analysis_figure.png", device = "png", width = 10, height = 10)

# Figure 5: Multiple regression between fish biomass (g/m2), kelp biomass (g/m2), kelp cover, rugosity, temperature in ggplot 
# combine all dataframes
```{r}
install.packages("devtools")
devtools::install_github("cardiomoon/ggiraphExtra", force = TRUE)
library(ggiraphExtra)

# Rename columns to remove spaces and special characters
names(all.params.data) <- c("Fish_Biomass", "Rugosity", "Kelp_Cover", "Kelp_Biomass", "predictions")

# Fit a multiple regression model
fit4 <- lm(Fish_Biomass ~ Rugosity * Kelp_Biomass * Kelp_Cover, data = all.params.data)

# Diagnostic plots for the regression model
par(mfrow=c(2,2))
plot(fit4)

# Use ggPredict to visualize the multiple regression plot interactively
interactive_plot <- ggPredict(fit4, interactive = TRUE)

# Save the interactive plot as an HTML file
htmlwidgets::saveWidget(interactive_plot, file = "output/figures/interactive_regression_plot.html")

Coefficients:
                                                   Estimate Std. Error t value Pr(>|t|)  
(Intercept)                                      -199.41221   96.09880  -2.075   0.0473 *
Rugosity                                           98.82780   36.09379   2.738   0.0106 *
`Kelp Biomass (g/cm2)`                              0.41643    0.18683   2.229   0.0340 *
`Kelp Cover (%)`                                 -765.82428  612.85640  -1.250   0.2218  
Rugosity:`Kelp Biomass (g/cm2)`                    -0.12496    0.05199  -2.403   0.0231 *
Rugosity:`Kelp Cover (%)`                         375.38109  244.24549   1.537   0.1355  
`Kelp Biomass (g/cm2)`:`Kelp Cover (%)`            -0.24978    0.91866  -0.272   0.7877  
Rugosity:`Kelp Biomass (g/cm2)`:`Kelp Cover (%)`   -0.05647    0.24991  -0.226   0.8229

# Try another type of multiple regession plot

```{r}
#fit multiple linear regression model
model2 <- lm(Fish_Biomass ~ Rugosity * Kelp_Biomass * Kelp_Cover, data = all.params.data)

#view results of model
summary_text <- capture.output(summary(model2))
writeLines(summary_text, "output/figures/summary_model.txt")

# Produce added variable plots
av_plots <- avPlots(model2)

#The x-axis displays a single predictor variable and the y-axis displays the response variable.
#The blue line shows the association between the predictor variable and the response variable, while holding the value of all other predictor variables constant.
#The points that are labelled in each plot represent the 2 observations with the largest residuals and the 2 observations with the largest partial leverage.
```
